Toxic code snippets on Stack Overflow

### 2017-10-23 cloverflow-tse/cloverflow.tex
Further improvements.

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 69 of them (34.5\%) have never been notified of
outdated code in the answers and 26 of them (19.8\%) rarely or never fix the outdated
code. Only 3 answerers explicitly include software license in their answers and
138 answerers (69\%) never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
Similar to the first example, the clone code snippet on Stack Overflow does not 
include its original Apache v.2.0 license.
%\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
%Stack Overflow.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
%\FIXME{Something is not right: First it says that variable renaming is
%  disabled, and later it is said that SourcererCC uses renaming.}
%All variable renaming are disabled to decrease the number of
%false positives since we aim for finding clones that are copied from open source
%projects with minimal modifications. 
The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There are 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC). The other 270 pairs (12\%) are 
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. They result in a better classification,
 i.e.~from UD to QS or EX.
%~\FIXME{Report \% of conflicts
% between TP vs.~FP classifications first, and then about evidence.}
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{c@{~~}p{7.35cm}}
		\toprule
		Patt. & Description \\ 
		\midrule
		QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\

		SQ & Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\

		EX & Cloned from an external source \textit{X} to Stack Overflow\newline (X $\rightarrow$ S). \\

		UD & Cloned from each other or from an external source
                     \textit{X} outside the project (unknown)\\
		\midrule
		BP & Boiler-plate or IDE auto-generated \\

@@

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples in questions and answers. % They
Due to an absence of a checking mechanism after the code has been copied to
Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
being outdated or violating the original software license. We present a study
incorporating several state-of-the-art tools and techniques to automatically
extract and filter detected online clone pairs between 72,365 Java code snippets
on Stack Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
Our investigation of the online clone pairs revealed strong evidence that 154
clones have been copied from a Qualitas project to Stack Overflow.  We found 101
of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
we found 214 code snippets on Stack Overflow that violate the license of their
original software. We surveyed 201 high-reputation Stack Overflow answerers
(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
code. Only 3 answerers explicitly include software licenses in their answers and
138 answerers (69\%) never check for licensing conflicts between their copied code
snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

@@

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are totally different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
Similar to the first example, the clone code snippet on Stack Overflow does not 
include its original Apache v.2.0 license.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There were 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC) \FIXME{How have
  they been resolved?}. 
Another 270 pairs (12\%) were
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. Resolving the conflicts lead to a better classification,
 i.e.~from UD to QS or EX.
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{c@{~~}p{7.35cm}}
		\toprule
		Patt. & Description \\ 
		\midrule
		QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S) \\

		SQ & Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q) \\

		EX & Cloned from an external source to Stack Overflow (X $\rightarrow$ S) \\

		UD & Cloned from each other or from an external source
                     outside the project (unknown)\\
		\midrule
		BP & Boiler-plate or IDE auto-generated \\

@@

% \begin{IEEEbiographynophoto}{Chaiyong Ragkhitwetsagul}
% Biography text here.
% \end{IEEEbiographynophoto}

% % if you will not have a photo at all:
% \begin{IEEEbiographynophoto}{Jens Krinke}
% Biography text here.
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Matheus Paixao}
% Biography text here.
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Giuseppe Bianco}
% Biography text here.
% \end{IEEEbiographynophoto}

% % insert where needed to balance the two columns on the last page with
% % biographies
% %\newpage

% \begin{IEEEbiographynophoto}{Rocco Oliveto}
% Biography text here.
% \end{IEEEbiographynophoto}
